Deep learning approaches on musical assisted-orchestration: an evaluation study

### 2020-05-11 paper/latex/paper.tex
Added plots

\begin{caption}
Orchestra for each $N$ used in the experiments.
\label{class_res}
\end{caption}
\end{table}

@@

>>>>

\begin{table}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
Instruments & \multicolumn{2}{c|}{$N=4$} & \multicolumn{2}{c|}{$N=5$}& \multicolumn{2}{c|}{$N=6$}& \multicolumn{2}{c|}{$N=7$}& \multicolumn{2}{c|}{$N=8$}& \multicolumn{2}{c|}{$N=9$}& \multicolumn{2}{c|}{$N=10$}\\
\cline{2-3} & C & R & C & R & C & R & C & R & C & R & C & R & C & R\\
\hline
All & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Hn & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Ob & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Vn & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Va & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Vc & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Fl & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Tbn & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Bn & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
TpC & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
ClBb & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
\hline
\end{tabular}

\begin{caption}
Best test accuracy obtained for each model and value of $N$ over the total number of epochs. The accuracy is computed using $f$ define in (\ref{eval}). The first row correspond to the overall accuracy of the model, regrouping all the instruments. C is CNN with LSTM, R is ResNet.
\label{class_res}
\end{caption}
\end{table}

@@

\section{Figures}

\begin{figure}
\includegraphics[scale=0.6]{figs/CNN4.png}
\end{figure}
\begin{figure}
\includegraphics[scale=0.6]{figs/CNN5.png}
\end{figure}
\begin{figure}
\includegraphics[scale=0.6]{figs/CNN6.png}
\end{figure}
\begin{figure}
\includegraphics[scale=0.6]{figs/CNN7.png}
\end{figure}
\begin{figure}
\includegraphics[scale=0.6]{figs/CNN8.png}
\end{figure}
\begin{figure}
\includegraphics[scale=0.6]{figs/CNN9.png}
\end{figure}
\begin{figure}
\includegraphics[scale=0.6]{figs/CNN10.png}
\end{figure}
